%% document class
\documentclass[14pt, a4paper]{extreport}

%% packages 
\input{settings/packages}

%% page settings 
\input{settings/page}

%% own commands 
\newcommand{\tbi}[1]{\textbf{\textit{#1}}}
\input{settings/macros}

%--------------------------------------------------------
\begin{document}

\input{content/title_page}

\pagestyle{plain}

\begin{abstract}
NeuraLearnAcademy - Revolutionizing Distance Learning with AI-Enhanced Tools

In response to the persistent challenges faced by learners in online education platforms, 
NeuraLearnAcademy emerges as an innovative solution, pioneering a paradigm 
shift in the landscape of distance learning.

This electronic platform harnesses the power of advanced technologies, specifically Large Language Model (LLM) and Machine Learning (ML), to address and overcome
the limitations inherent in existing online learning environments. It introduces a suite of tools and features meticulously designed to enhance the learning experience.

The platform tackles the issues of low engagement through interactive elements
such as quizzes and discussions. It addresses the inadequacies of assessment methods by incorporating a range of evaluation techniques, ensuring a comprehensive understanding of the course material.
\end{abstract}
    
\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
    We would like to take this opportunity to express our sincere
    appreciation and best wishes to our devoted supervisor, Dr. Jehad,
    for her great leadership and ongoing motivation during the completion of
    this project. The assistance, and guidance she occasionally provided will
    help us get far along in the life's journey we are about to take.

    We also take this occasion to thank Faculty of Computers and
    Artificial Intelligence Council for their support and work in getting us all
    the resources we need.

    We would especially like to thank the FCAI members for the useful
    information they gave in their respective domains.
    Finally, we express our gratitude to Almighty, our parents, and
    everyone who has provided assistance, encouragement, and support.
\end{abstract}

    

\tableofcontents 
\listoffigures
\listoftables

\include{chapters/chapter1}
\include{chapters/chapter2}
\include{chapters/chapter3}
\include{chapters/chapter4}


\end{document}
